---
# Title
title: "Title"

# Add additional authors in a hyphenated list
author:
- Author

# Date of publication (to be adjusted by editorial team)
date: 2020-01-30T01:00:00+01:00

# Categories (to be adjusted by editorial team)
categories: 
  - tutorials
  
# Tags (to be adjusted by editorial team)
tags: 
  - R

# bib-file (optional)
# bibliography: 
---

<!-- 
Please specify all required packages in the pkgs vector
Note: Please assign a name (such as "packages") to each code chunk 
-->
```{r packages, echo=FALSE, results='hide', message=FALSE, include=FALSE, eval=TRUE}
## Save package names as a vector of strings
pkgs <- c()

## Install uninstalled packages
lapply(pkgs[!(pkgs %in% installed.packages())], install.packages)

## Load all packages to library and adjust options
lapply(pkgs, library, character.only = TRUE)
```

<!-- 
One introductory paragraph for the blog post: 
Topic, presenter, workshop, relevance 
-->
The topic ABC has become really important. In this [Methods Bites Tutorial](https://www.mzes.uni-mannheim.de/socialsciencedatalab/categories/tutorials/), [AUTHOR](https://twitter-or-web-site) (AUTHOR'S INSTITUTION) offers a hands-on recap of their workshop "WORKSHOP TITLE" in the [MZES Social Science Data Lab](https://www.mzes.uni-mannheim.de/socialsciencedatalab/page/events/) in SEMESTER YEAR.

<!-- Optional: One paragraph on learning objectives -->
After reading this blog post and engaging with the applied exercises, readers should:

 - be able to ...
 
<!-- If applicable: Note with references on related materials -->
*Note:* This blog post provides a summary of AUTHOR's workshop in the [MZES Social Science Data Lab](https://www.mzes.uni-mannheim.de/socialsciencedatalab/page/events/). The original workshop materials, including slides and scripts, are available from our [GitHub](https://github.com/SocialScienceDataLab/...).
A live recording of the workshop is available on our [YouTube Channel](https://www.youtube.com/channel/UCnM2zpHYdOH521e1uwajKrw).

<!-- 
Generate an overview of the article 
Note: Section anchors are generated automatically from section headings as 
      hyphenated lower-case labels without special characters; e.g. a section
      title "Why R?" will result in the anchor "#why-r".
-->
### Overview
1. [**First section**](#first-section)
1. [**Second section**](#second-section)
    1. [First subsection](#first-subsection)
    1. [Second subsection](#second-subsection)
        1. [First subsubsection](#fist-subsubsection)
1. [**Further reading**](#further-reading)


### First section
<!-- Add some text here  -->

```{r chunk-name, echo=FALSE, results='hide', message=FALSE, include=FALSE}
```

### First section
<!-- Add some text here  -->

### Second section
<!-- Add some text here  -->

<details> 
<summary>Code for XX</summary> 
```{R code1, eval=FALSE}
```
</details>

##### First subsection
<!-- Add some text here  -->

##### Second subsection
<!-- Add some text here  -->

###### First subsubsection
<!-- Add some text here  -->


<details> 
<summary>Code for XX</summary> 
```{R code 2, eval=FALSE}
```
</details>

<!-- Add a list of further readings -->
### Further readings <a name="furtherreadings"></a>

* [Reference](http://)

<!-- Add something about the instructor -->
### About the presenter 

<!-- Optional: Add references (if bib-file is specified) -->
### References

